Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2021-09-02 paper/SupMat.Rnw
uncommentedout sweave and put in code chunck to load M and rho and place them in where needed

\begin{document}
\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
%<<eval=T,echo=F,message=F,warning=F>>=
%system(paste("biber", sub("\\.Rnw$", "", current_input())))

%#place R code here for loading in necessary variables from Results
%#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
%allregres<-matrix(rnorm(10),2,5)
%@

@@

When needed, noise with symmetric tail association was generated by taking a very large sample (100000) 
%***DAN: Dan, later, check whether 100000 is what was actually used. I'm thinking we could probably do a million.
of left-tail associated noise generated as 
described above, and then calculating the Pearson correaltion coefficient, $\rho$, of the sample.
Symmetric noise $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$ for $i=1,...,M$ was then generated 
from the bivariate normal distribution $N\left(\vec{0}, \Sigma \right)$, where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, 
and then we set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

@@

First, for a large integer $M$ (we used $M=$),
%***DAN: Jasmin, please fill in the value, 1000000 or bigger if you can swing it
carry out the following steps once.
\begin{enumerate}
\item Generate $M$ independent points $u^{(k)}$, $k=1,\ldots,M$, from a standard normal distribution.
\item Generate $M$ independent points $(\tilde{b}_i^{(k)},\tilde{b}_j^{(k)})$, as in SI section \ref{sect:noise}, which are left-tail associated
and which have standard-normal marginals. 
\item Again as in SI section \ref{sect:noise}, generate $M$ independent points $(\tilde{\ddot{b}}_i^{(k)},\tilde{\ddot{b}}_j^{(k)})$, 
$k=1,\ldots,M$, from a bivariate normal distribution with component variances $1$ and Pearson correlation the same as 
$(\tilde{b}_i^{(k)},\tilde{b}_j^{(k)})$.
\end{enumerate}
These data are stored and used repeatedly below. This provides computational efficiency because 
random number generation is computationally expensive.

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}
\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
<<eval=T,echo=F,message=F,warning=F>>=
#system(paste("biber", sub("\\.Rnw$", "", current_input())))

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
@

@@

When needed, noise with symmetric tail association was generated by taking a very large sample (\Sexpr{M}) 
%***DAN: Dan, later, check whether 100000 is what was actually used. I'm thinking we could probably do a million.
of left-tail associated noise generated as 
described above, and then calculating the Pearson correaltion coefficient, $\rho$, of the sample.
Symmetric noise $\left(\tilde b_1^{(i)},\tilde b_2^{(i)}\right)$ for $i=1,...,M$ was then generated 
from the bivariate normal distribution $N\left(\vec{0}, \Sigma \right)$, where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, 
and then we set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

@@

First, for a large integer $M$ (we used $M=\Sexpr{M}$),
carry out the following steps once.
\begin{enumerate}
\item Generate $M$ independent points $u^{(k)}$, $k=1,\ldots,M$, from a standard normal distribution.
\item Generate $M$ independent points $(\tilde{b}_i^{(k)},\tilde{b}_j^{(k)})$, as in SI section \ref{sect:noise}, which are left-tail associated
and which have standard-normal marginals. 
\item Again as in SI section \ref{sect:noise}, generate $M$ independent points $(\tilde{\ddot{b}}_i^{(k)},\tilde{\ddot{b}}_j^{(k)})$, 
$k=1,\ldots,M$, from a bivariate normal distribution with component variances $1$ and Pearson correlation the same as 
$(\tilde{b}_i^{(k)},\tilde{b}_j^{(k)})$.
\end{enumerate}
These data are stored and used repeatedly below. This provides computational efficiency because 
random number generation is computationally expensive.
